---
title: "Create an R package workflow"
output: html_notebook
---

This document shows the set-up steps for a new R package using the {devtools}/{usethis} framework which will include the following features:

 - version controlled by git and hosted on GitHub
 
 - {pkgdown} site
 
 - Automated GitHub actions checks for R CMD build, with README badge
 
 - Unit testing using {testthat}
 
 - Automated GitHub actions for code testing using CodeCov and {covr}
 
 - README built in .Rmd
 

## Initial Set-up

### 1. Check the package name is available:

```{r}
available::available("sdtmval")
```


### 2. Create a new directory:

```{r}
# dir.create("sdtmval")
```


### 3. Set-up the directory as an R package:

```{r}
create_package("sdtmval")
```


### 4. Populate the DESCRIPTION file

Update these fields:
 
 - Title
 
 - Authors (if not automated)
 
 - Description
 
 - Chose a license:

```{r}
use_mit_license()
```

## Add Git/GitHub

### 5. Set-up local version control

```{r}
use_git()
```

Next, make your first commit using the terminal.

```{bash}
git status
```

```{bash}
git add .
git commit -m "initial commit"
```


### 6. Connect to GitHub remote repository

```{r}
use_github()
```






















